Dynamics of the Lower Solar Atmosphere

### 2024-07-22 chapter2/ms.tex
Updates from Overleaf

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Solar Dynamic Observatory}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The Solar Dynamics Observatory \citep[SDO;][]{sdo} is a NASA mission designed to understand the causes of solar variability at various spatiotemporal and wavelength scales, as well as its impacts on Earth and the near-Earth environment. It is part of NASA’s Living With a Star program and houses multiple instruments onboard to address its numerous scientific goals. Among the numerous instruments on-board {\it SDO}, we have extensively used data from two instruments – the Atmospheric Imaging Assembly (AIA) and the Helioseismic and Magnetic Imager (HMI).

@@

AIA \citep{aia} obtains full-disk images of the solar transition region and corona at unprecedented spatio-temporal resolution. The field of view (FOV) covers up to 0.5 $\mathrm{R_{\odot}}$ above the limb. It incorporates several filters at 94 {\AA}, 131 {\AA}, 171 {\AA}, 193 {\AA}, 211 {\AA} and 335 {\AA}, mainly probing the Corona, along with filters at 304 {\AA}, 1600 {\AA}, 1700 {\AA}, and 4500 {\AA}, mainly observing the Chromosphere and Photosphere, providing a total temperature coverage range of 0.06 MK to 20 MK and across various heights. Figure 2.1 illustrates the temperature responses of these filters (Boerner et al., 2012), derived based on the CHIANTI model for solar emissivity (Dere et al., 1997, 2009). Under different conditions, these AIA filters observe different plasma phenomena \citep{o'dwyer10}. Typical exposure times range between 0.5 and 3 seconds. Each AIA telescope is accompanied by its own guide telescope to ensure highly accurate image stabilization. For ous analysis, we have extensively used the coronal EUV channel observations from AIA, e.g. 94 {\AA}, 131 {\AA}, 171 {\AA}, 193 {\AA}, 211 {\AA} and 335 {\AA}. These coronal channels observations are usually available with a 12 s cadence.

@@

The Interface Region Imaging Spectrograph \citep[IRIS;][]{iris} is a NASA small satellite explorer mission designed to observe the dynamics of the lower solar atmosphere. IRIS contains a spectrograph and a slit-jaw imager (SJI), observing the chromosphere, the transition region, and the lower corona. It primarily observes the Sun in two passbands around 1400 {\AA} and 2800 {\AA}. IRIS provides data at high spatial resolution (0.33 {\arcsec} in FUV and 0.4 {\arcsec} in NUV), high time cadence (up to 1 second), and high spectral resolution (12 or 25 m{\AA} per pixel).

@@

 STIX \citep{stix,stix1} is designed to study the Sun's X-ray emissions, providing crucial insights into the processes driving solar flares and other high-energy phenomena. STIX incorporates a set of collimators and detectors to capture high-resolution images of the Sun in X-rays. These images allow scientists to pinpoint the locations and intensities of X-ray emissions associated with solar flares. The instrument covers a broad range of X-ray energies, from approximately 4 to 150 keV, enabling it to observe various aspects of solar activity. STIX can capture X-ray data with high temporal resolution, allowing scientists to study the rapid evolution of solar flares and other transient events in detail. STIX works synergistically with other instruments onboard Solar Orbiter, providing complementary measurements to enhance our understanding of the Sun's dynamic behaviour across different wavelengths and energy ranges.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{The Solar Ultraviolet Imaging Telescope}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{itemize}
    \item dynamic coupling between the lower and the middle solar atmosphere
    \item measurement of solar spectral radiance in the NUV.
    \item spectral energy distribution of solar flares in NUV
    \item dynamics of chromospheric eruptive phenomena at various spatiotemporal scales
    \item Initiation of Coronal Mass Ejections(CMEs) and space weather: the kinematics of erupting prominences during the early phase.
\end{itemize}

@@

The Solar Ultraviolet Imaging Telescope \citep[SUIT;][]{ghosh16,article} is one of the seven payloads onboard the Aditya-L1 mission \citep{adityal1} of the Indian Space Research Organization (ISRO). With its 11 science filters (3 broadband and eight narrowband), SUIT will have the capability to probe different heights of solar atmosphere in photosphere and chromosphere to help us understand the various processes that transport mass and energy from one layer to another. SUIT will provide full disk as well as partial disk images of the Sun with a pixel size of 0.7". Through SUIT imaging, we would be able to resolve solar flares spatially on the surface of the Sun, for the first time in near ultra-violet (NUV), which will help us to address the questions regarding their build-up and triggering mechanism. In addition, to measure the spatially resolved solar spectral irradiance within the wavelength range that is central for studying the Chemistry of oxygen and ozone in the Stratosphere of Earth's atmosphere.

@@

The origin of the WLFs, i.e., the physical process responsible for generating the continuum and its contribution to the overall energy distribution, is still highly uncertain. The question remains whether WLFs are photospheric phenomena due to $H^{-}$ free-free emission or chromospheric phenomena due to H free-bound emission. The more recent studies further constrain the origin of the WLFs to be Chromospheric phenomena, as it has been shown that the WL and HXR footpoint centroids are cospatial. Similarly, \cite{krucker15} constrained the cospatial WL and HXR footpoints within the chromosphere for three flares. With the help of SUIT, we would be able to localize the WL flares and resolve them on various parts of the Solar disk, which along with observations from Interface Region Imaging Telescope (IRIS), Helioseismic and Magnetic Imager (HMI), would help us localize the source of the WL footpoints and also comment on the formation mechanism of the WL itself.

@@

The spectral energy distribution of flares is one of the critical areas of interest in the physics of flares. A complete understanding of this will help us decode the physical processes involved in solar flares and help quantify their effects on solar spectral irradiance. Ideally, it would be essential to observe flares at all wavelengths simultaneously with sufficient spatiotemporal resolution to figure out the spectral energy distribution of flares. Unfortunately, this is generally not the case, and we have to rely on the sporadic observations made using ground-based instruments in the visible domain. As mentioned earlier, the majority of the flare energy is emitted in the NUV and visible domain. \cite{kretzschmar10,kretzschmar11}, performed statistical studies using a large number of flare observations across a wide energy range. They demonstrated, at the peak of the flare, about 70\% of the total energy was radiated in the continuum visible and NUV channel as illustrated in \ref{tab1}. SUIT would observe and resolve the solar flares within 200-400 nm using 8 NBs and 3 BBs. This, along with IRIS data, would help us comment on the energy distribution of flares of various classes.

@@

Finally, one of the major question of interest is how the Solar flares affect the Spectral Solar Irradiance (SSI) and Total Solar Irradiance (TSI) variability from a short to much longer, Solar Cycle timescale. \cite{kretzschmar10,kretzschmar11} performed statistical studies using a large number of flare observations across a wide energy range. For this purpose, they used the full Sun observations of Solar flux from Solar and Heliospheric Observatory (SoHO), three visible Solar irradiances from VIRGO/Solar Photometer (SPM) passbands centred on 402 nm, 500 nm, and 862 nm, respectively, from 1996 to 2008. Additionally, they also use the EUV irradiance in the ranges 0.1-50 nm and 26-34 nm measured by SOHO/Solar EUV Monitor \citep{judge98} and SXR measurements from GOES satellites. They showed that stacked TSI variation profiles during solar flares show variation at more than 2 sigma level during the peak flare time, indicating the presence of flare signals in the TSI measurements.

\begin{figure}[h!]
    \centering
    \includegraphics[width = \linewidth]{Figures/nphys1741_page-0002.jpg}
    \caption{Averaged TSI variations during flares. The TSI time-series averages over four exclusive sets of solar flares of decreasing amplitude. The black and pink curves correspond respectively to the TSI measured by the PMOV6 and the DIARAD radiometers. The dashed lines correspond to the 95\% confidence levels, while the vertical line denotes the peak time of the flare \citep{kretzschmar10}.}
    \label{fig2}
\end{figure}

>>>>

\justifying

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Solar Dynamics Observatory}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The Solar Dynamics Observatory \citep[SDO;][]{sdo} is a NASA mission designed to understand the causes of solar variability at various spatio temporal and wavelength scales, as well as its impacts on Earth and the near-Earth environment. It is part of NASA’s Living With a Star program and houses multiple instruments onboard to address its numerous scientific goals. Among the numerous instruments on-board {\it SDO}, we have extensively used data from two instruments – the Atmospheric Imaging Assembly (AIA) and the Helioseismic and Magnetic Imager (HMI).

@@

AIA \citep{aia} obtains full-disk images of the solar transition region and corona at unprecedented spatio-temporal resolution. The field of view (FOV) covers up to 0.5 $\mathrm{R_{\odot}}$ above the limb. It incorporates several filters at 94 {\AA}, 131 {\AA}, 171 {\AA}, 193 {\AA}, 211 {\AA} and 335 {\AA}, mainly probing the Corona, along with filters at 304 {\AA}, 1600 {\AA}, 1700 {\AA}, and 4500 {\AA}, mainly observing the Chromosphere and Photosphere, providing a total temperature coverage range of 0.06 MK to 20 MK and across various heights. Figure 2.1 illustrates the temperature responses of these filters \citep{borner12}, derived based on the CHIANTI model for solar emissivity \citep{chianti,chianti1}. Under different conditions, these AIA filters observe different plasma phenomena \citep{o'dwyer10}. Typical exposure times range between 0.5 and 3 seconds. Each AIA telescope is accompanied by its own guide telescope to ensure highly accurate image stabilization. For ous analysis, we have extensively used the coronal EUV channel observations from AIA, e.g. 94 {\AA}, 131 {\AA}, 171 {\AA}, 193 {\AA}, 211 {\AA} and 335 {\AA}. These coronal channels observations are usually available with a 12 s cadence.

@@

The Interface Region Imaging Spectrograph \citep[IRIS;][]{iris} is a NASA small satellite explorer mission designed to observe the dynamics of the lower solar atmosphere. IRIS contains a spectrograph and a slit-jaw imager (SJI), observing the chromosphere, the transition region, and the lower corona. It primarily observes the Sun in two pass bands around 1400 {\AA} and 2800 {\AA}. IRIS provides data at high spatial resolution (0.33 {\arcsec} in FUV and 0.4 {\arcsec} in NUV), high time cadence (up to 1 second), and high spectral resolution (12 or 25 m{\AA} per pixel).

@@

 STIX \citep{stix,stix1} is designed to study the Sun's X-ray emissions, providing crucial insights into the processes driving solar flares and other high-energy phenomena. STIX incorporates a set of collimators and detectors to capture high-resolution images of the Sun in X-rays. These images allow scientists to pinpoint the locations and intensities of X-ray emissions associated with solar flares. The instrument covers a broad range of X-ray energies, from approximately 4 to 150 keV, enabling it to observe various aspects of solar activity. STIX can capture X-ray data with high temporal resolution, allowing scientists to study the rapid evolution of solar flares and other transient events in detail. STIX works together with other instruments onboard Solar Orbiter, providing complementary measurements to enhance our understanding of the Sun's dynamic behaviour across different wavelengths and energy ranges.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{The Solar Ultraviolet Imaging Telescope}\label{sec:suit}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{itemize}
    \item dynamic coupling between the lower and the middle solar atmosphere
    \item measurement of solar spectral radiance in the NUV.
    \item spectral energy distribution of solar flares in NUV
    \item dynamics of chromospheric eruptive phenomena at various spatio temporal scales
    \item Initiation of Coronal Mass Ejections(CMEs) and space weather: the kinematics of erupting prominence during the early phase.
\end{itemize}

@@

The Solar Ultraviolet Imaging Telescope \citep[SUIT;][]{ghosh16,article} is one of the seven payloads onboard the Aditya-L1 mission \citep{adityal1} of the Indian Space Research Organization (ISRO). With its 11 science filters (3 broadband and eight narrow band), SUIT will have the capability to probe different heights of solar atmosphere in photosphere and chromosphere to help us understand the various processes that transport mass and energy from one layer to another. SUIT will provide full disk as well as partial disk images of the Sun with a pixel size of 0.7". Through SUIT imaging, we would be able to resolve solar flares spatially on the surface of the Sun, for the first time in near ultra-violet (NUV), which will help us to address the questions regarding their build-up and triggering mechanism. In addition, to measure the spatially resolved solar spectral irradiance within the wavelength range that is central for studying the Chemistry of oxygen and ozone in the Stratosphere of Earth's atmosphere.

@@

The origin of the WLFs, i.e., the physical process responsible for generating the continuum and its contribution to the overall energy distribution, is still highly uncertain. The question remains whether WLFs are photospheric phenomena due to $H^{-}$ free-free emission or chromospheric phenomena due to H free-bound emission. The more recent studies further constrain the origin of the WLFs to be Chromospheric phenomena, as it has been shown that the WL and HXR foot point centroids are cospatial. Similarly, \cite{krucker15} constrained the cospatial WL and HXR foot points within the chromosphere for three flares. With the help of SUIT, we would be able to localize the WL flares and resolve them on various parts of the Solar disk, which along with observations from Interface Region Imaging Telescope (IRIS), Helioseismic and Magnetic Imager (HMI), would help us localize the source of the WL foot points and also comment on the formation mechanism of the WL itself.

@@

The spectral energy distribution of flares is one of the critical areas of interest in the physics of flares. A complete understanding of this will help us decode the physical processes involved in solar flares and help quantify their effects on solar spectral irradiance. Ideally, it would be essential to observe flares at all wavelengths simultaneously with sufficient spatio temporal resolution to figure out the spectral energy distribution of flares. Unfortunately, this is generally not the case, and we have to rely on the sporadic observations made using ground-based instruments in the visible domain. As mentioned earlier, the majority of the flare energy is emitted in the NUV and visible domain. \cite{kretzschmar10,kretzschmar11}, performed statistical studies using a large number of flare observations across a wide energy range. They demonstrated, at the peak of the flare, about 70\% of the total energy was radiated in the continuum visible and NUV channel as illustrated in \ref{tab1}. SUIT would observe and resolve the solar flares within 200-400 nm using 8 NBs and 3 BBs. This, along with IRIS data, would help us comment on the energy distribution of flares of various classes.

@@

Finally, one of the major question of interest is how the Solar flares affect the Spectral Solar Irradiance (SSI) and Total Solar Irradiance (TSI) variability from a short to much longer, Solar Cycle timescale. \cite{kretzschmar10,kretzschmar11} performed statistical studies using a large number of flare observations across a wide energy range. For this purpose, they used the full Sun observations of Solar flux from Solar and Heliospheric Observatory (SoHO), three visible Solar irradiances from VIRGO/Solar Photometer (SPM) pass bands centred on 402 nm, 500 nm, and 862 nm, respectively, from 1996 to 2008. Additionally, they also use the EUV irradiance in the ranges 0.1-50 nm and 26-34 nm measured by SOHO/Solar EUV Monitor \citep{judge98} and SXR measurements from GOES satellites. They showed that stacked TSI variation profiles during solar flares show variation at more than 2 sigma level during the peak flare time, indicating the presence of flare signals in the TSI measurements.

\begin{figure}[h!]
    \centering
    \includegraphics[width = \linewidth]{Figures/nphys1741_page-0002.webp}
    \caption{Averaged TSI variations during flares. The TSI time-series averages over four exclusive sets of solar flares of decreasing amplitude. The black and pink curves correspond respectively to the TSI measured by the PMOV6 and the DIARAD radiometers. The dashed lines correspond to the 95\% confidence levels, while the vertical line denotes the peak time of the flare \citep{kretzschmar10}.}
    \label{fig2}
\end{figure}
